---
title: "Covid91 vaccine study Final2020"
author: "Jeanette Serrano"
date: "Nov 16,2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode aids to say covid and then remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
```

# Introduction



<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

```{r}
dataF<- filter(FinalData, sex== "gal") 
```


### Graphical Results for Gals   

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
barchartGC(~infected + treatment,data= dataF)
barchartGC(~infected + treatment,data= dataF, type="percent",main="females")

```

  
### Numerical Summaries for Gals 

```{r}
table1 <- xtabs(~infected + treatment, data=dataF)
rowPerc(table1)
colPerc(table1)
```
### Inferential Results for Gals 

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
### Graphical Results for Guys   



### Numerical Summaries for Guys 

### Inferential Results for Guys 

### Graphical Results for LGBTQ  



### Numerical Summaries for LGBTQ

### Inferential Results for LGBTQ





### Graphical Results for DrugUsers   



### Numerical Summaries for DrugUsers 

### Inferential Results for DrugUsers

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
